The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba

### 2020-12-03 README.Rmd
updating master.zip

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- 'The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba'

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- 'The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba'

@@

You can download the compendium as a zip from from this URL:
[master.zip](https://github.com/sheilarm23/rrcompendium/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

### 2020-12-03 analysis/paper/paper.Rmd
updating master.zip

# INSTALLING PACKAGES AND LIBRARIES - if needed
packages = c("BiocManager", "raster", "ggplot2", "ggthemes", "here",  
             "rentrez", "ape", "seqinr", "phangorn")

>>>>

# INSTALLING PACKAGES AND LIBRARIES - if needed
packages = c("BiocManager", "raster", "ggplot2", "ggthemes", "mapproj", "here",  
             "rentrez", "ape", "seqinr", "phangorn")
